DOpElib:\\ Differential Equations and Optimization Environment

### 2021-07-27 Examples/OPT/StatPDE/Example8/content.tex
Added Benchmark fracture examples - and spellcheck in content files

\subsubsection{Program description}
In this example, we have now some local (point) constraints, local constraints and a global
constraint. In constrast to the previous example, these 
constraints are all taken care of in the 
\texttt{localconstraints.h} file. 
Specifically, the point constraints are handled by the 
\texttt{DOpE::PointConstraints<...>} function, which is also initializad 
in the main file.

>>>>

\subsubsection{Program description}
In this example, we have now some local (point) constraints, local constraints and a global
constraint. In contrast to the previous example, these 
constraints are all taken care of in the 
\texttt{localconstraints.h} file. 
Specifically, the point constraints are handled by the 
\texttt{DOpE::PointConstraints<...>} function, which is also initialized 
in the main file.

### 2021-07-27 Examples/PDE/InstatPDE/Example11/content.tex
Added Benchmark fracture examples - and spellcheck in content files

In this example, we consider a lower-dimensional fracture in a
  $2$-dimensional domain. This fracture has 
a constant length and varying width.
The driving force in this example is a given constant pressure prescribed in the fracture.
The setting is motivated by the book of Sneddon and Lowengrub
\cite{sneddon1969crack} and therefore known as `Sneddon' benchmark or `pressure-driven cavity'. Analytical solutions are derived in \cite{sneddon1969crack} and are also discussed in 
\cite{bourdin2012variational}. Subsequently, 
\cite{wheeler2014augmented,heister2015primal} coin the proposed benchmark, 
and provide numerical results.\\

@@

\begin{Problem}[Euler-Lagrange System]
Find $(u,\varphi) \in \mathcal{V} \times \mathcal{W}$ with
\begin{align*}
\left( \left((1-\kappa)\varphi^2 + \kappa\right) \sigma(u),e(w)\right)+(\varphi^2 p,\Div w)=0\quad \forall w \in \mathcal{V},
\end{align*}
and
\begin{align*}
(1- \kappa)(&\varphi \sigma(u):e(u),\psi-\varphi) + 2(\varphi p \Div u,\psi-\varphi)\\
+&\ G_C\left(-\frac{1}{\epsilon}(1-\varphi,\psi-\varphi)+\epsilon\left(\nabla \varphi,\nabla(\psi-\varphi)\right) \right)\geq 0\quad \forall \psi \in \mathcal{W}_{\text{in}} \cap L^{\infty}(\Omega).
\end{align*}
\end{Problem}
The crack irreversibilty condition is handled via a Lagrange multiplier as in Example 5.2.8.\\

In this example, we are especially interested in three computed quantities:
\begin{itemize}
 \item The \textbf{total crack volume} (TCV) can be computed numerically using
\begin{align}
\label{eq_TCV_num}
\text{TCV}_{h,\epsilon}=\int_{\Omega} u(x,y) \cdot \nabla \varphi(x,y)\ \mathrm{d}{(x,y)}.
\end{align}
A formula for the limit can be obtained using \cite{sneddon1969crack}.
Using symmetry of the configuration, i.e., $u_y(x,0^+) = - u_y(x,0^-)$,
and the known crack location $[-1,1]\times \{0\}$, one obtains
\begin{align*}
\text{TCV}_{2D}=2 \int_{-\infty}^{\infty} u_y (x,0^+)\ \mathrm{d}x,
\end{align*}
where $0^\pm$ denotes the respective limit from above or below, and
$u_y$ denotes the second ($y$) component of the displacement.

Using the exact representation of $u_y$ (cf. \cite{sneddon1969crack}, page
29)
\[
u_y(x,0^+) =  \frac{p l_0}{E^{\prime}} \left(1-\frac{x^2}{l_0^2}\right)^{1/2}
\]
we obtain:
\begin{align}
\label{eq_TCV_exact}
 \text{TCV}_{2D}  
= \int_{-\infty}^{\infty} 2 u_y (x,0^+)\ \mathrm{d}x 
= \frac{2\pi p l_0^2}{E^{\prime}}.
\end{align}
Applied to our parameter settings, we consequently
obtain the reference value for an infinite domain as:
\[
\text{TCV}_{2D} \approx 6.03186\times 10^{-3}.
\]

@@

Further details on this numerical example can be found in \cite[Chapter 7]{schroder2020selection}.

>>>>

In this example, we consider a lower-dimensional fracture in a
  $2$-dimensional domain. This fracture has 
a constant length and varying width.
The driving force in this example is a given constant pressure prescribed in the fracture.
The setting is motivated by the book of Sneddon and Lowengrub
\cite{SneddLow69} and therefore known as `Sneddon' benchmark or `pressure-driven cavity'. Analytical solutions are derived in \cite{SneddLow69} and are also discussed in 
\cite{bourdin2012variational}. Subsequently, 
\cite{WeWiWo2014,HeWheWi15} coin the proposed benchmark, 
and provide numerical results.\\

@@

\begin{Problem}[Euler-Lagrange System]
Find $(u,\varphi) \in \mathcal{V} \times \mathcal{W}$ with
\begin{align*}
\left( \left((1-\kappa)\varphi^2 + \kappa\right) \sigma(u),e(w)\right)+(\varphi^2 p,\Div w)=0\quad \forall w \in \mathcal{V},
\end{align*}
and
\begin{align*}
(1- \kappa)(&\varphi \sigma(u):e(u),\psi-\varphi) + 2(\varphi p \Div u,\psi-\varphi)\\
+&\ G_C\left(-\frac{1}{\epsilon}(1-\varphi,\psi-\varphi)+\epsilon\left(\nabla \varphi,\nabla(\psi-\varphi)\right) \right)\geq 0\quad \forall \psi \in \mathcal{W}_{\text{in}} \cap L^{\infty}(\Omega).
\end{align*}
\end{Problem}
The crack irreversibility condition is handled via a Lagrange multiplier as in Example~\ref{PDE_phase_field_fracture}\\

In this example, we are especially interested in three computed quantities:
\begin{itemize}
 \item The \textbf{total crack volume} (TCV) can be computed numerically using
\begin{align}
\label{eq_TCV_num}
\text{TCV}_{h,\epsilon}=\int_{\Omega} u(x,y) \cdot \nabla \varphi(x,y)\ \mathrm{d}{(x,y)}.
\end{align}
A formula for the limit can be obtained using \cite{SneddLow69}.
Using symmetry of the configuration, i.e., $u_y(x,0^+) = - u_y(x,0^-)$,
and the known crack location $[-1,1]\times \{0\}$, one obtains
\begin{align*}
\text{TCV}_{2D}=2 \int_{-\infty}^{\infty} u_y (x,0^+)\ \mathrm{d}x,
\end{align*}
where $0^\pm$ denotes the respective limit from above or below, and
$u_y$ denotes the second ($y$) component of the displacement.

Using the exact representation of $u_y$ (cf. \cite{SneddLow69}, page
29)
\[
u_y(x,0^+) =  \frac{p l_0}{E^{\prime}} \left(1-\frac{x^2}{l_0^2}\right)^{1/2}
\]
we obtain:
\begin{align}
\label{eq_TCV_exact}
 \text{TCV}_{2D}  
= \int_{-\infty}^{\infty} 2 u_y (x,0^+)\ \mathrm{d}x 
= \frac{2\pi p l_0^2}{E^{\prime}}.
\end{align}
Applied to our parameter settings, we consequently
obtain the reference value for an infinite domain as:
\[
\text{TCV}_{2D} \approx 6.03186\times 10^{-3}.
\]

@@

Further details on this numerical example can be found in \cite[Chapter~7]{SchroederEtAl:2021}.
